\huge Fusion Moves for Correlation Clustering

### 2015-05-26 paper/poster.tex
added inital poster

            Correlation clustering~\cite{Bansal-2002}, or multicut partitioning~\cite{chopra_1993_mp} ,
            is widely used partitioning an undirected graph with positive and negative edge weights
            ~\cite{andres_2011_iccv,kroeger_2012_eccv,yarkony_2012_eccv,alush_2013_simbad}.
            Since it is NP-hard, exact solvers do not scale and approximative solvers often give bad results.
            Inspired by \cite{Lempitsky-2010} Here we define fusion moves for the correlation clustering problem.
            Our algorithm iteratively fuses the current and a proposed partitioning which  monotonously improves
            the partitioning and maintains a valid partitioning at all times.
            Furthermore, it scales to larger datasets, gives near optimal solutions, and at the same time shows
            a good anytime performance.

@@

            \end{block}
            \vfill

@@

            \begin{block}{Results}
            Among all proposed solvers, Fusion-HC-MC has the best overall anytime performance. With increasing problems
            size (9b-9e and 9f) the runtimes of MC-I, MC-R and CGC increase drastically, while the proposed solvers still scale well.

            \includegraphics[width=0.9\linewidth]{res_images.pdf}

            \end{block}
            \vfill
            \begin{block}{Evaluation by Variation of Information (VI) and Rand Index (RI)}
              \centering
              \includegraphics[width=0.8\linewidth]{virib.pdf}            
            \end{block}
            \vfill
            % \begin{block}{Conclusions}
            %     We have presented a fast and scalable 
            %     approximate solver for correlation 
            %     clustering, named Correlation Clustering Fusion (CC-Fusion).
            %     It is orthogonal to previous research, \ie it can be combined with
            %     any correlation clustering solver.
            %     %
            %     The best solution is iteratively improved 
            %     by a fusion with proposal solutions.
            %     The fusion move itself is formulated as correlation
            %     clustering on a smaller graph with fewer edges and nodes
            %     and can therefore be solved much faster than the original problem.
            %     %
            %     Our evaluation shows that several CC-Fusion algorithms
            %     outperform state-of-the-art solvers w.r.t. anytime performance 
            %     with increasing problem size.
            % \end{block}
            \vfill
            \begin{block}{References}
                \small
                \bibliographystyle{ieee}
                \bibliography{egbib}
            \end{block}
            \vfill
          }
          % ---------------------------------------------------------%
          % end the column
        \end{minipage}
      \end{beamercolorbox}
    \end{column}
    % ---------------------------------------------------------%
    % end the column
  \end{columns}
  \vskip1ex
  %\tiny\hfill\textcolor{ta2gray}{Created with \LaTeX \texttt{beamerposter}  \url{http://www-i6.informatik.rwth-aachen.de/~dreuw/latexbeamerposter.php}}
  %\tiny\hfill{Created with \LaTeX \texttt{beamerposter}  \url{http://www-i6.informatik.rwth-aachen.de/~dreuw/latexbeamerposter.php} \hskip1em}
\end{frame}
\end{document}

>>>>

            Correlation clustering~\cite{Bansal-2002}, or multicut partitioning~\cite{chopra_1993_mp} ,
            is widely used partitioning an undirected graph with positive and negative edge weights
            ~\cite{andres_2011_iccv,kroeger_2012_eccv,yarkony_2012_eccv,alush_2013_simbad}.
            Since it is NP-hard, exact solvers do not scale and approximative solvers often give bad results.
            Inspired by \cite{Lempitsky-2010} Here we define fusion moves for the correlation clustering problem.
            Our algorithm iteratively fuses the current and a proposed partitioning which  monotonously improves
            the partitioning. It scales well gives near optimal solutions, and has
            a good anytime performance.

@@

            \end{block}
            \vfill
            \begin{block}{Proposal Generators}

            As discussed in~\cite{Lempitsky-2010}, proposals
            should have two properties: \emph{high quality} 
            and \emph{large diversity}.
            For correlation clustering fusion we add a third
            property: \emph{size}.
            We use the following two proposal generators (see paper for details):
            \begin{itemize}
                \item \textbf{Randomized Hierarchical Clustering (RHC):}
                we add normally distributed noise  $\mathcal{N}(0, \sigma_{ehc})$ to each edge weight.
                In each step the edge with the highest weight is contracted.

                \item \textbf{Randomized Watersheds (RWS):}
                The edge weighted watershed algorithm~\cite{meyer_2013}
                with random seeds can be used to find
                cheap proposals.
            \end{itemize}

@@

            \begin{block}{Results}
            Among all proposed solvers, Fusion-HC-MC has the best overall anytime performance.
            \includegraphics[width=0.9\linewidth]{res_images.pdf}

            \end{block}
            \vfill
            \begin{block}{Evaluation by Variation of Information (VI) and Rand Index (RI)}
              \centering
              \includegraphics[width=0.7\linewidth]{virib.pdf}            
            \end{block}
            \vfill
            % \begin{block}{Conclusions}
            %     We have presented a fast and scalable 
            %     approximate solver for correlation 
            %     clustering, named Correlation Clustering Fusion (CC-Fusion).
            %     It is orthogonal to previous research, \ie it can be combined with
            %     any correlation clustering solver.
            %     %
            %     The best solution is iteratively improved 
            %     by a fusion with proposal solutions.
            %     The fusion move itself is formulated as correlation
            %     clustering on a smaller graph with fewer edges and nodes
            %     and can therefore be solved much faster than the original problem.
            %     %
            %     Our evaluation shows that several CC-Fusion algorithms
            %     outperform state-of-the-art solvers w.r.t. anytime performance 
            %     with increasing problem size.
            % \end{block}
            \vfill
            \begin{block}{References}
                \footnotesize
                \bibliographystyle{ieee}
                \bibliography{egbib}
            \end{block}
            \vfill
          }
          % ---------------------------------------------------------%
          % end the column
        \end{minipage}
      \end{beamercolorbox}
    \end{column}
    % ---------------------------------------------------------%
    % end the column
  \end{columns}
  \vskip1ex
  %\tiny\hfill\textcolor{ta2gray}{Created with \LaTeX \texttt{beamerposter}  \url{http://www-i6.informatik.rwth-aachen.de/~dreuw/latexbeamerposter.php}}
  %\tiny\hfill{Created with \LaTeX \texttt{beamerposter}  \url{http://www-i6.informatik.rwth-aachen.de/~dreuw/latexbeamerposter.php} \hskip1em}
\end{frame}
\end{document}
